Participatory Mashups: Using Users to make Data Mashable

### 2008-09-26 papers/cscw_mash/cscw_mash.tex
Minor paper changes, and working on the data store

Much of the most interesting information on the web is available as unstructured natural language text: arguments, ideas, opinions, factual claims, jokes. Much of this is information that could benefit a lot from being mashed up. For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''.

Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting. For example, tables of data that have been entered by hand, or one of the many tiny web services that display data from a database backend using their own custom template that nobody has ever written a scraper for.

In this approach we argue for ``participatory mashups'' as a way to open up access to this data. In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and connecting information in new ways. By teaching a participatory mashup the meaning of some data, the user helps themselves, since they can now include this data in their mashup, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.

We motivate this approach using two mashup tools that we have built. Think Link allows users to identify factual claims that they read on web pages and connect them to related factual claims on other sites, including claims that may oppose the original claim. Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example improvements provided by users.

>>>>

Much of the most interesting information on the web is available as unstructured natural language text: arguments, ideas, opinions, factual claims, jokes. Much of this is information that could benefit a lot from being mashed up. For example ``which of these claims is likely to be wrong?'', ``what other sites disagree with this opinion?'', ``is there a more reliable source that backs up this claim?'', or ``what ideas on this site would I be likely to find most interesting?''. While natural language processing techniques have achieved a lot, understanding such information in a fully automated way is hard.

Similarly, there is a lot of structured information stored in the ``long tail'' of web sites that are too small for it to be worth a mashup author writing a custom scraper or API interface for, but which may nonetheless be very interesting. For example, tables of data that have been entered by hand, or one of the many tiny web sites that display data from a database backend using their own custom template that nobody has ever written a scraper for.

In this paper we argue for ``participatory mashups'' as a way to open up access to this data. In a participatory mashup we blur the line between the users and creators of a mashup by allowing the users of a mashup to teach the mashup how to understand new information, and how to connect information in new ways. By teaching a participatory mashup the meaning of some data, the user helps themselves, since the new information becomes part of the mashup they are interacting with, but they also help the wider community of users, since all other users can now benefit from the system understanding this data.

We motivate this approach using two mashup tools that we have built. Think Link allows a user to identify factual claims on web pages, and uses this information to expose users to opposing points of view. Mash Maker allows users to teach it the meaning of structured data on arbitrary web sites, and then enhances these web sites to make them more useful, guided by example improvements provided by users.
